\newpage
\chapter*{Appendices}
\addcontentsline{toc}{chapter}{\numberline{}Appendices}

\section*{Appendix 1: PowerWise Information}
\addcontentsline{toc}{section}{\numberline{}Appendix 1: PowerWise Information}
\par Enclosed in this appendix are some examples and information about the PowerWise monitoring service and its interface. This is the power monitoring system that is being used in the Sudbury Public Housing Development. The data comes from ammeters that are hooked into the circuit breaker panel of the house. Those ammeters wirelessly transmit their readings to a server every minute, so minute by minute data is available to be inspected and analyzed in real time. If all the ammeters are connected and labeled properly, it is possible to differentiate between appliances and get powerful insights.

\newpage
\addtocounter{page}{1}
\section*{Appendix 2: Example Case Study}
\addcontentsline{toc}{section}{\numberline{}Appendix 2: Example Case Study}
\par Enclosed in this appendix is the example case study that was provided to us by the DOER. This case study acted as a guideline and template when we created case studies for the three project sites that we focused on.

\newpage
\addtocounter{page}{2}
\section*{Appendix 3: Interview Questions}
\addcontentsline{toc}{section}{\numberline{}Appendix 3: Interview Questions}
% stuff

\newpage
\addtocounter{page}{9}
\section*{Appendix 4: On-site Information Gathering Guides}
\addcontentsline{toc}{section}{\numberline{}Appendix 4: On-site Information Gathering Guides}
% stuff

\newpage
\addtocounter{page}{13}
\section*{Appendix 5: Our Case Studies}
\addcontentsline{toc}{section}{\numberline{}Appendix 5: Our Case Studies}
\par Enclosed in this appendix are the case studies that we produced for the DOER as the project deliverables.


\newpage
\addtocounter{page}{6}
\section*{Appendix 6: Summative Assessment}
\addcontentsline{toc}{section}{\numberline{}Appendix 6: Summative Assessment}


