%*******************************************************
% Bibliography
%*******************************************************

\newpage
\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{\numberline{}Bibliography}
\setlength{\parindent}{0pt}

\hangindent=0.5in
Amherst College. (2014). \emph{The Bunker Pellet Boiler Project RTDE Application}. Massachusetts, United States Amherst College. \\

\hangindent=0.5in
Balaras, C. A., Droutsa, K., Dascalaki, E., \& Kontoyiannidis, S. (2005). \emph{Heating Energy Consumption and Resulting Environmental Impact of European Apartment Buildings}. Energy and Buildings, 37(5), 429-442. \\

\hangindent=0.5in
BEAM Engineering. (2014). \emph{Southern Berkshire Regional School Renewable Thermal Heating – Biomass}. Massachusetts, United States: BEAM Engineering. \\

\hangindent=0.5in
Botkin, D. B., Keller, E. A., \& Rosenthal, D. B. (2012). \emph{Environmental science}. Retrieved 04\slash 10\slash 2015, from http:\slash \slash ic.ucsc.edu\slash ~wxcheng\slash envs23\slash BotkinCH19.pdf \\

\hangindent=0.5in
Brunk, C. G. (2006). \emph{Public knowledge, public trust: understanding the'knowledge deficit'}. Community genetics, 9(3), 178-183. \\

\hangindent=0.5in
Chung, W., Hui, Y., \& Lam, Y. M. (2006). \emph{Benchmarking the energy efficiency of commercial buildings}. Applied Energy, 83(1), 1-14. \\

\hangindent=0.5in
Chwieduk, D. (2003). \emph{Towards sustainable-energy buildings}. Applied Energy, 76(1), 211-217. \\

\hangindent=0.5in
Conservation Law Foundation. (2010). \emph{Green Communities Act}. Retrieved April 5, 2015, from http:\slash \slash www.clf.org\slash our-work\slash clean-energy-climate-change\slash energy-efficiency\slash green-communities-act-ma\slash  \\

\hangindent=0.5in
D. C. Architects, (2014). \emph{MSBA Acceleratd Repair Program Boiler Replacement Study} \slash  Schematic Design. Southern Berkshire Regional School District: Dietz \& Company Architects. \\

\hangindent=0.5in
Desideri, U., \& Proietti, S. (2002). \emph{Analysis of energy consumption in the high schools of a province in central Italy}. Energy and Buildings, 34(10), 1003-1016. \\

\hangindent=0.5in
DOER: Massachusetts Department of Energy. (2015). \emph{SAPHIRE Schools Renewable Thermal Program: Technical Assistance with Feasbility Studies.} \\

\hangindent=0.5in
Downing, M., Eaton, L. M., Graham, R. L., Langholtz, M. H., Perlack, R. D., Turhollow Jr, A. F., . . . Brandt, C. C. (2011). \emph{U.S. Billion-Ton Update: Biomass Supply for a Bioenergy and Bioproducts Industry}.(pp. Medium: ED). \\

\hangindent=0.5in
DSIRE. (2015). \emph{Green Technology Programs}. Retrieved April 5, 2015, from http:\slash \slash programs.dsireusa.org\slash system\slash program?state=MA \\

\hangindent=0.5in
EEA. (2015). \emph{Renewable Energy Funding and Incentives}. Retrieved 04\slash 28\slash 2015, from Renewable Energy Funding and Incentives \\

\hangindent=0.5in
EEA. (2015). Massachusetts’ Progress towards Reducing Greenhouse Gas (GHG) Emissions by 2020. from http:\slash \slash www.mass.gov\slash eea\slash air-water-climate-change\slash climate-change\slash massachusetts-global-warming-solutions-act\slash  \\

\hangindent=0.5in
EERE. (2015). \emph{Office of Energy Efficiency \& Renewable Energy}. Retrieved April 5, 2015, from http:\slash \slash energy.gov\slash eere\slash better-buildings-neighborhood-program\slash better-buildings-partners) \\

\hangindent=0.5in
EIA. (2015). \emph{Household Energy Use in Massachusetts}. In U.S. Energy Information Administration (Ed.). eia.gov. \\

\hangindent=0.5in
Ervin, C. A. (1994). \emph{Energy efficiency, renewable energy and sustainable development: Illinois Univ.}, Chicago, IL (United States). Energy Resources Center. \\

\hangindent=0.5in
Filippın, C. (2000). \emph{Benchmarking the energy efficiency and greenhouse gases emissions of school buildings in central Argentina. Building and Environment}, 35(5), 407-414. \\

\hangindent=0.5in
Fitzgerald, J. (2014). {Utilities may limit new natural gas connections}. \\

\hangindent=0.5in
Gold, R. (2015). \emph{The boom: how fracking ignited the American energy revolution and changed the world}: Simon and Schuster. \\

\hangindent=0.5in
Haines, A., Kovats, R. S., Campbell-Lendrum, D., \& Corvalán, C. (2006). \emph{Climate change and human health: Impacts, vulnerability and public health}. Public health, 120(7), 585-596. \\

\hangindent=0.5in
Holdren, J. P., Smith, K. R., Kjellstrom, T., Streets, D., Wang, X., \& Fischer, S. (2000). Energy, the environment and health. \emph{New York: United Nations Development Programme.} \\

\hangindent=0.5in
Kampa, M., \& Castanas, E. (2008). \emph{Human health effects of air pollution. Environmental pollution}, 151(2), 362-367. \\

\hangindent=0.5in
Karlstrøm, H., \& Ryghaug, M. (2014). Public attitudes towards renewable energy technologies in Norway. The role of party preferences. Energy policy, 67, 656-663. \\

\hangindent=0.5in
Kohler Adam, P. E. (2014). \emph{Massachusetts Department of Energy Resources -Feasibility Study for Amherst College - Bunker Building}. Massachusetts: Kohler\&Lewis Engineering. \\

\hangindent=0.5in
Krawczyk, D. A. (2014). Theoretical and real effect of the school's thermal modernization—a case study. \emph{Energy and Buildings}, 81, 30-37. \\

\hangindent=0.5in
Lis, P. (2013). The actual and calculated thermal needs of educational buildings. \emph{Environmental Engineering IV}, 405. \\

\hangindent=0.5in
Maehlum, M. A. (2014). Solar Energy Pros and Cons. Retrieved 04\slash 17\slash 2015, 2015, from http:\slash \slash energyinformative.org\slash solar-energy-pros-and-cons\slash  \\

\hangindent=0.5in
Mass.gov. (2015). Energy and Environmental Affairs. Retrieved April 5, 2015, from http:\slash \slash www.mass.gov\slash eea\slash  \\

\hangindent=0.5in
Mass.gov. (2015). Renewable Energy Funding and Incentives. Retrieved April 5, 2014, from http:\slash \slash www.mass.gov\slash eea\slash energy-utilities-clean-tech\slash renewable-energy\slash renewable-energy-funding\slash  \\

\hangindent=0.5in
Massachusetts Clean Energy Center. (2015). Mass CEC. Retrieved April 5, 2015, from http:\slash \slash www.masscec.com\slash  \\

\hangindent=0.5in
Massachusetts Department of Energy Resources. (2015). Solar Hot Water Heating System. Retrieved 04\slash 21\slash 2015, from http:\slash \slash www.mass.gov\slash eea\slash docs\slash doer\slash renewables\slash thermal\slash about-solar-thermal-handout.pdf \\

\hangindent=0.5in
Massachusetts Department of Energy Resources. (2015). Geothermal Ground-Source Heat Pump. Retrieved 04\slash 21\slash 2015, from http:\slash \slash www.mass.gov\slash eea\slash docs\slash doer\slash renewables\slash thermal\slash about-geothermal-heat-pumps-handout.pdf \\

\hangindent=0.5in
Massachusetts Department of Energy Resources. (2015). Biomass Heating System. Retrieved 04\slash 21\slash 2015, from http:\slash \slash www.mass.gov\slash eea\slash docs\slash doer\slash renewables\slash thermal\slash about-biomass-handout.pdf \\

\hangindent=0.5in
Massachusetts Department of Energy Resources. (2015). Retrieved 04\slash 21\slash 2015, from http:\slash \slash www.mass.gov\slash eea\slash  \\

\hangindent=0.5in
Massachusetts School Building Authority. (2011). Green Schools. Retrieved April 5, 2015, from http:\slash \slash www.massschoolbuildings.org\slash programs\slash green\_schools \\

\hangindent=0.5in
McMichael, A. J., Campbell-Lendrum, D. H., Corvalán, C. F., Ebi, K. L., Githeko, A. K., Scheraga, J. D., \& Woodward, A. (2003). \emph{Climate change and human health: risks and responses}: World Health Organization. \\

\hangindent=0.5in
National Renewable Energy Laboratory. (2014). Monthly Solar Insolation. Retrieved 4\slash 27\slash 15, from http:\slash \slash www.nrel.gov\slash gis\slash solar.html \\

\hangindent=0.5in
Nguyen, C. T., Kai; Wong, Yechan. (2014). REACHING ZERO-NET ENERGY AT WATER AND WASTEWATER TREATMENT FACILITIES. \\

\hangindent=0.5in
Office of Energy Efficiency \& Renewable Energy. (2015). Buildings. Retrieved 04\slash 28\slash 2015, from http:\slash \slash energy.gov\slash eere\slash efficiency\slash buildings \\

\hangindent=0.5in
Office of Response and Restoration. (2015). How Oil Harms Animals and Plants in Marine Environments. Retrieved 05\slash 02\slash 2015, from http:\slash \slash response.restoration.noaa.gov\slash oil-and-chemical-spills\slash oil-spills\slash how-oil-harms-animals-and-plants.html \\

\hangindent=0.5in
Paksoy, H., Andersson, O., Abaci, S., Evliya, H., \& Turgut, B. (2000). Heating and cooling of a hospital using solar energy coupled with seasonal thermal energy storage in an aquifer. \emph{Renewable Energy}, 19(1), 117-122. \\

\hangindent=0.5in
Parida, B., Iniyan, S., \& Goic, R. (2011). A review of solar photovoltaic technologies. \emph{Renewable and sustainable energy reviews}, 15(3), 1625-1636. \\

\hangindent=0.5in
Pérez-Lombard, L., Ortiz, J., \& Pout, C. (2008). A review on buildings energy consumption information. \emph{Energy and Buildings}, 40(3), 394-398. \\

\hangindent=0.5in
Rabl, A., \& Spadaro, J. V. (2000). Public health impact of air pollution and implications for the energy system. \emph{Annual review of Energy and the Environment}, 25(1), 601-627. \\

\hangindent=0.5in
RDK Engineers. (2014). \emph{Mount Everett Regional High School Roof and Boiler Study}. Amherst, Massachusetts: RDK Engineers. \\

\hangindent=0.5in
Renewable Energy Success Stories. (2015). Renewable Energy Success Stories. Retrieved April 22, 2015, from http:\slash \slash www.revermont.org\slash main\slash technology\slash renewable-energy-success-stories\slash  \\

\hangindent=0.5in
Rezaie, B., Dincer, I., \& Esmailzadeh, E. (2013). Energy options for residential buildings assessment. \emph{Energy Conversion and Management}, 65, 637-646. \\

\hangindent=0.5in
Rezaie, B., Esmailzadeh, E., \& Dincer, I. (2011). Renewable energy options for buildings: case studies. \emph{Energy and Buildings}, 43(1), 56-65. \\

\hangindent=0.5in
Samimi, A., \& Zarinabadi, S. (2012). Reduction of greenhouse gases emission and effect on environment. \emph{Journal of American Science}, 8(8), 1011-1015. \\

\hangindent=0.5in
Shafiee, S., \& Topal, E. (2009). When will fossil fuel reserves be diminished? \emph{Energy policy}, 37(1), 181-189. \\

\hangindent=0.5in
Sharp, T. R. (1998). \emph{Benchmarking energy use in schools.} Paper presented at the Proceedings of the ACEEE 1998 Summer Study on Energy Efficiency in Buildings (3. \\

\hangindent=0.5in
Southern Berkshire Regional School District. (2010). \emph{Requirements for EECBG Final Project Report - Sub Grants}. Sheffield, Massachusetts: Southern Berkshire Regional School District. \\

\hangindent=0.5in
Spyropoulos, G. N., \& Balaras, C. A. (2011). Energy consumption and the potential of energy savings in Hellenic office buildings used as bank branches—a case study. \emph{Energy and Buildings,} 43(4), 770-778. \\

\hangindent=0.5in
U.S. Department of Energy. (2001). Air-Source Heat Pumps. Retrieved 04\slash 28\slash 2015, from http:\slash \slash nrec.mn\slash data\slash uploads\slash Nom\%20setguul\%20xicheel\slash Heat\%20pump\slash Air\%20source\%20heat\%20pump.pdf \\

\hangindent=0.5in
U.S. Department of Energy. (2012). Operating and Maintaining Your Heat Pump. from http:\slash \slash energy.gov\slash energysaver\slash articles\slash operating-and-maintaining-your-heat-pump \\

\hangindent=0.5in
U.S. Energy Information Administration. (2013). EIA projects world energy consumption will increase 56\% by 2040. Retrieved 04\slash 27\slash 2015, from http:\slash \slash www.eia.gov\slash todayinenergy\slash detail.cfm?id=12251 \\

\hangindent=0.5in
U.S. Energy Information Administration. (2014). Levelized Cost and Levelized Avoided Cost of New Generation Resources in the Annual Energy Outlook 2014. Retrieved 04\slash 17\slash 2015, from http:\slash \slash www.eia.gov\slash forecasts\slash aeo\slash pdf\slash electricity\_generation.pdf , http:\slash \slash www.renewable-energysources.com \\

\hangindent=0.5in
U.S. National Climate Assesment. (2014). Climate Change Impacts in the United States: The Third National Climate Assessment. Retrieved 04\slash 27\slash 2015, from http:\slash \slash nca2014.globalchange.gov\slash report\slash our-changing-climate\slash observed-change\#intro-section-2 \\

\hangindent=0.5in
WaitButWhy. (2015). How Tesla Will Change The World. from http:\slash \slash waitbutwhy.com\slash 2015\slash 06\slash how-tesla-will-change-your-life.html\#part1 \\

\hangindent=0.5in
Wilson Engineering. (2015). \emph{Boiler System Sizing Review for Southern Berkshire Regional School District}. Massachusetts, United States: Wilson Engineering Services. \\

\hangindent=0.5in
Yang, H., Cui, P., \& Fang, Z. (2010). Vertical-borehole ground-coupled heat pumps: a review of models and systems. \emph{Applied Energy}, 87(1), 16-27.

\setlength{\parindent}{0.25in}
